DOpElib:\\ Differential Equations and Optimization Environment

### 2014-10-24 Examples/Documentation/introduction.tex

\section{License information}
Copyright (C) 2012 by the DOpElib authors\\[2mm]
%
This file is part of DOpElib\\[2mm]
%
DOpElib is free software: you can redistribute it
and/or modify it under the terms of the GNU General Public
License as published by the Free Software Foundation, either
version 3 of the License, or (at your option) any later
version.\\[2mm]
%
DOpElib is distributed in the hope that it will be
useful, but WITHOUT ANY WARRANTY; without even the implied
warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
PURPOSE.  See the GNU General Public License for more
details.\\[2mm]
%
Please refer to the file LICENSE.TXT included in this distribution
for further information on this license.

@@

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item Unpack in your preferred directory:
\begin{lstlisting}
~/Software/> tar -xzf dopelib-1.0.tar.gz
\end{lstlisting}
to get
\begin{lstlisting}
~/Software/dopelib-1.0
\end{lstlisting}
To build the \texttt{DOpElib} you have to change to the directory 
\texttt{DOpEsrc} where you can call 
\begin{lstlisting}
~/Software/dopelib-1.0/DOpEsrc> make all
\end{lstlisting}
to build the library. You also get various installation options by just typing 
\texttt{make}.
\item To generate documentation, please go into:
\begin{lstlisting}
~/Software/dopelib-1.0/Examples
\end{lstlisting}
Here, you get all options by typing:
\begin{lstlisting}
make
\end{lstlisting}
Specifically, you can create and run all examples, running a test suite,
and generating documentation:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    all       :  Make all examples (in optimized mode)                   =
=    allignore :  Make all examples (in optimized mode), ignore errors.   =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    cat       :  Run clean, run all, run tests (combine these commands)  =
=    catignore :  Same as cat, but ignores compiler errors.               =
=    pdf-doc   :  Create documentation in pdf file format via latexmk     =
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
For html documentation, change into:
\begin{lstlisting}
~/Software/dopelib-1.0/doxygen
\end{lstlisting}
and then typing \texttt{make}. Doxygen documentation
will require either 
latex or doxygen to be installed on your computer.
\item If you wish to test if everything worked. To do so you can 
change to the \texttt{Examples} directory and \texttt{make tests} which will give you a 
list of all the examples and whether they behave as expected by the library, see also 
Chapter~\ref{chap:test}.
\item  If you want to use some of the supported third party libraries install them and follow 
 the instructions in \texttt{ThirdPartyLibs/README}. There may be further information 
 in some \texttt{ThirdPartyLibs/*.INSTALLNOTES} that you may want to
 consider.\\[3mm]
 As example, the installation of ipopt works as follows:\\
In the path \texttt{~/dope/ThirdPartyLibs>} type in the terminal\\
\texttt{./install-free-libs.sh}

>>>>

\section{License information}
Copyright (C) 2012--2014 by the DOpElib authors\\[2mm]
%
This file is part of DOpElib\\[2mm]
%
DOpElib is free software: you can redistribute it
and/or modify it under the terms of the GNU General Public
License as published by the Free Software Foundation, either
version 3 of the License, or (at your option) any later
version.\\[2mm]
%
DOpElib is distributed in the hope that it will be
useful, but WITHOUT ANY WARRANTY; without even the implied
warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
PURPOSE.  See the GNU General Public License for more
details.\\[2mm]
%
Please refer to the file LICENSE.TXT included in this distribution
for further information on this license.

@@

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item Unpack in your preferred directory:
\begin{lstlisting}
~/Software/> tar -xzf dopelib-2.0.tar.gz
\end{lstlisting}
to get
\begin{lstlisting}
~/Software/dopelib-2.0
\end{lstlisting}
To build the \texttt{DOpElib} you have to change to the directory 
\texttt{DOpEsrc} where you can call 
\begin{lstlisting}
~/Software/dopelib-2.0/DOpEsrc> make all
\end{lstlisting}
to build the library. You also get various installation options by just typing 
\texttt{make}.
\item To generate documentation, please go into:
\begin{lstlisting}
~/Software/dopelib-2.0/Examples
\end{lstlisting}
Here, you get all options by typing:
\begin{lstlisting}
make
\end{lstlisting}
Specifically, you can create and run all examples, running a test suite,
and generating documentation:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    all       :  Make all examples (in optimized mode)                   =
=    allignore :  Make all examples (in optimized mode), ignore errors.   =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    cat       :  Run clean, run all, run tests (combine these commands)  =
=    catignore :  Same as cat, but ignores compiler errors.               =
=    pdf-doc   :  Create documentation in pdf file format via latexmk     =
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
For html documentation, change into:
\begin{lstlisting}
~/Software/dopelib-2.0/doxygen
\end{lstlisting}
and then typing \texttt{make}. Doxygen documentation
will require either 
latex or doxygen to be installed on your computer.
\item If you wish to test if everything worked. To do so you can 
change to the \texttt{Examples} directory and \texttt{make tests} which will give you a 
list of all the examples and whether they behave as expected by the library, see also 
Chapter~\ref{chap:test}.
\item  If you want to use some of the supported third party libraries install them and follow 
 the instructions in \texttt{ThirdPartyLibs/README}. There may be further information 
 in some \texttt{ThirdPartyLibs/*.INSTALLNOTES} that you may want to
 consider.\\[3mm]
 As example, the installation of ipopt works as follows:\\
In the path \texttt{~/dope/ThirdPartyLibs>} type in the terminal\\
\texttt{./install-free-libs.sh}
